Converting LaTeX R Journal Articles into Rmarkdown using texor and rebib

### 2023-07-13 texor.Rmd
tried to make the paper organised, so it is easier to fill in

# Background

### Pandoc does the heavy-lifting

Pandoc is a versatile document conversion program written in Haskell that is core
to numerous documentation systems, including Rmarkdown and Quarto. Pandoc first 
converts a document into an abstract syntax tree. From this, it can convert to a
different format, including custom ones. Although creating bespoke writers/readers
in Lua can be challenging, pandoc includes filters that allow users to customize 
the output generated based on matching patterns plus some logic to modify them.

The \CRANpkg{texor} package uses these filters heavily, even for simple tasks like choosing
which supporting figures to copy. A Lua filter constructs a list of image paths, 
stores them momentarily and the package uses this data to copy images.

### Pre-Processing : Regular Expressions

@@

### Post-Processing : Lua Filters

@@

LaTeX, Regex, pandoc
building blocks of the packages, methods used in them [MOW]

# Converting LaTeX to Markdown

## Also mention the hard parts
## Lua Filters with pandoc
A lot of details about different components of \CRANpkg{texor}

# Managing bibliography using \CRANpkg{rebib}

@@

# Getting started

 Examples/ getting started / usage and so on

@@

# Supplementary materials
 github repos for the packages, rjtools

>>>>

# Converting from LaTeX to R Markdown

The decision to convert to R Markdown format means that the output to pdf and HTML will depend on Pandoc [@pandoc]. 
Pandoc is a versatile document conversion program written in Haskell that is core to numerous documentation systems, including Rmarkdown and Quarto. Pandoc first converts a document into an abstract syntax tree. From this, it can convert to a different format, including custom ones. Although creating bespoke writers/readers in `Lua` can be challenging, pandoc includes filters that allow users to customize the output generated based on matching patterns plus some logic to modify them.

**DC: Can you explain what a Lua filter is?**

The \CRANpkg{texor} package uses these filters heavily, even for simple tasks like choosing which supporting figures to copy. A `Lua` filter constructs a list of image paths, stores them momentarily and the package uses this data to copy images. However, \CRANpkg{texor} also includes many pre-processing functions that employ regular expressions. This is needed to convert some text and LaTeX commands that are not recognized or handled by Pandoc.

**DC: Add a diagram here showing flow of work, just pre-process .tex -> pandoc -> lua ???**

**Maybe more details on the supporting packages here: LaTeX, Regex, pandoc building blocks of the packages, methods used in them [MOW]**

## Pre-processing using regular expressions

@@

**Be sure to mention the hard parts**

## Post-Processing : Lua Filters

@@

# Structure of the \CRANpkg{texor} package

**DC: List the main functions in an organised way, could be the pre-processing functions, the post-processing functions, utility functions. This can be also be summarized in a table, but there needs to be text explanations of the main functionality.**

# Using \CRANpkg{texor}

**Install instructions**

**Examples / getting started / usage and so on**

# Managing the bibliography using \CRANpkg{rebib}

## Overview

@@

## Using \CRANpkg{rebib}

**Install instructions**

**Examples / getting started / usage and so on**

@@

# Supplementary materials

 github repos for the packages, texor, rebib, rjtools
